### 2022-01-27 input/experiments.tex
few changes on subsection C

\begin{figure*}
  \subfloat {
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  }
  \hspace{5pt}
  \subfloat {
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{\label{fig:europe-ases}Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC in an Edge
    infrastructure comprising 40 interconnected autonomous systems of
    1157 \processes spanning across Europe~\cite{knight2011internet}}
\end{figure*}

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks by using another
    Edge infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} as depicted in the left
    Figure~\ref{fig:europe-ases}. \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent The left Figure~\ref{fig:europe-ases} depicts the
    operations executed during the simulation that lasts 7 seconds: at
    1 second, a \node located in Lisbon, Portugal performs an
    \texttt{Add}; at 2 seconds, a \node located in Palma de Majorque,
    Spain performs an \texttt{Add}; at 3 seconds, a \node located in
    Paris, France performs an \texttt{Add}; at 4 seconds, a \node
    located in Hvanneyri, Iceland performs an \texttt{Add};
    finally at 5 seconds, the \node in Spain performs a \texttt{Del}.

    \noindent We evaluate \NAME against \NAMEC. Using \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

    \noindent We measure the number of messages transiting through the
    network for each operation, and we measure the number of
    \processes that maintain an index (\ie that belong to a partition)
    over time.

  \item[Results:] The right of Figure~\ref{fig:europe-ases} shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
    \texttt{Add} costs an order of magnitude more with \NAME compared
    to \NAMEC.  \NAME's messages propagate through all Europe, for
    \NAME regards Europe as 1 network of 1157 \processes while
    \NAMEC's messages propagate through Portugal's network of 23
    \processes only.

    \noindent Figure~\ref{fig:europe-ases} shows that Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    gateway in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, hence the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's gateway echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

    \noindent Figure~\ref{fig:europe-ases} highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
    updates France's 39 \processes.

    \noindent Figure~\ref{fig:europe-ases} shows that Iceland's
    \texttt{Add} has similar cost for \NAME and \NAMEC. Indeed, they
    both update Iceland, and when the notifications reach Copenhagen
    in Danemark, they stop either because France's notifications are
    closer (\NAME) or the Danish network does not have any source
    (\NAMEC).

>>>>

\begin{figure*}
  \subfloat[An infrastructure composed of 40 interconnected autonomous systems and
    1157 \processes spanning across Europe~\cite{knight2011internet}]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf} 
  }
  \hspace{5pt}
  \subfloat[Traffic overhead and indexes
    maintained by \NAME and its extension \NAMEC]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.pdf}
  }
  \caption{\label{fig:europe-ases} Comparison between \NAME and \NAMEC}
\end{figure*}

@@

\subsection{Cross autonomous systems}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures composed of multilple autonomous systems and
    discuss an improvement called \underline{cross} \underline{\NAME}
    (\NAMEC). At coarse-grained, \NAMEC enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the  additional two pages available in the
    camera-ready version of the article.} dynamic partitioning by
    allowing AS' gateways to stop notifications when their respective
    network does not appear to have a source.

  \item[Description:] We build a network of networks by using another
    Edge infrastructure comprising 1157 \processes distributed in 40
    interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet} \note{Ici c'est Géant aussi. pourquoi nous n'avions pas 40 ASes dans l'experience précedente + Mentionné que c'est une vision de Geant?}
     as depicted in Figure~\ref{fig:europe-ases} (a). \emph{Gateway} \processes (dark in
    the figure) link autonomous systems together, \eg a Lisbon \node
    links Portugal to Spain and United Kingdoms through a Madrid \node
    and a London \node respectively.

    \noindent Figure~\ref{fig:europe-ases} (a) also depicts the
    operations executed during the 7 seconds simulation: at 1 second,
    a \node located in Lisbon, Portugal performs an \texttt{Add} (\ie
    Lisbon becomes a new source); at 2 seconds, a \node located in
    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
    \node located in Paris, France performs an \texttt{Add}; at 4
    seconds, a \node located in Hvanneyri, Iceland performs an
    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
    \texttt{Del} (the Spanish source is removed). Each \node has been
    chosen in order to illustrate the limitation of \NAME and so the
    interest of containning the propagation within an AS as proposed by
    \NAMEC.

    \noindent In \NAMEC, each
    \process maintains a \emph{local} index that corresponds to the
    best partition of its autonomous systems, and a \emph{global}
    index that corresponds to the best partition cross autonomous
    systems, \ie adjacent autonomous systems that have at least one
    source.

    \noindent To compare \NAME against \NAMEC, we measure the number of messages transiting through the
    network for each operation, as well as the number of
    \processes that maintain an index (\ie that belong to a partition)
    over time.

  \item[Results:] Figure~\ref{fig:europe-ases} (b) shows the
    results of this experiment. The top part highlights the cost of
    each partitioning protocol after each operation, while the bottom
    part provides the insight that explains these costs by displaying
    the number of indexes maintained by each protocol.

    \noindent Figure~\ref{fig:europe-ases} shows that Portugal's
    \texttt{Add} costs an order of magnitude more with \NAME compared
    to \NAMEC.  \NAME's messages propagate through all Europe, for
    \NAME regards Europe as a single network of 1157 \processes while
    \NAMEC's messages propagate through Portugal's network of 23
    \processes only.
    % 
    \noindent  Spain's
    \texttt{Add} costs slightly more with \NAMEC compared to \NAME.  A
    gateway in Madrid links Portugal to Spain and the rest of
    Europe. Since Lisbon is closer to Madrid than Palma de Majorque
    is, only 11 \processes in Spain actually need to receive and
    deliver the new notification, which explains the small overhead of this
    operation with \NAME. Using \NAMEC, the overhead is slightly
    higher since
    \begin{inparaenum}[(i)]
    \item the 20 \processes of Spain's network need to receive and
      deliver the new notification, \emph{and}
    \item Madrid's gateway echoes Lisbon's notification as soon as it
      receives Palma's notification to 11 \processes.
    \end{inparaenum}

    \noindent Figure~\ref{fig:europe-ases} also highlights the worst
    case scenario of \NAME: the cost of France's \texttt{Add} is close
    to that of Portugal's \texttt{Add} since it updates the whole
    Europe excluding Portugal and Spain. On the opposite, \NAMEC only
    updates France's 39 \processes.

    \noindent The last \texttt{Add} operation in Iceland has similar
    cost for \NAME and \NAMEC. Indeed, they both update Iceland, and
    when the notifications reach Copenhagen in Danemark, they stop
    either because France's notifications are closer (\NAME) or the
    Danish network does not have any source (\NAMEC).
